Formalization of Network Flow Algorithms

### 2017-02-28 paper/root.tex

  \begin{figure}[!h]
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

@@

      \addplot table {
        1000 .005   
        1500 .013  
        2000 .024  
        2500 .037  
        3000 .066 
        3500 .077 
        4000 .096 
        4500 .146 
        5000 .194 
        5500 .192    
      }; \addlegendentry{prpu-SML, sparse};

      \addplot table {
        1000 .053   
        1500 .089   
        2000 .091   
        2500 .120 
        3000 .256 
        3500 .210 
        4000 .265 
        4500 .499 
        5000 .457 
        5500 .522     
      }; \addlegendentry{prpu-Java2, sparse};

      \addplot table {
        1000 .014 
        1500 .029 
        2000 .027 
        2500 .037 
        3000 .043 
        3500 .051 
        4000 .053 
        4500 .080 
        5000 .084 
        5500 .085 
      }; \addlegendentry{prpu-Java1, sparse};

      \addplot table {
        1000 .006 
        1500 .013
        2000 .014
        2500 .019
        3000 .041
        3500 .035
        4000 .042
        4500 .076
        5000 .079
        5500 .082    
      }; \addlegendentry{prpu-C++, sparse};

      \addplot table {
        1000 0  
        1500 .001  
        2000 .003  
        2500 .002  
        3000 .003  
        3500 .004  
        4000 .005  
        4500 .007  
        5000 .010 
        5500 .009      
      }; \addlegendentry{prpu-C, sparse};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {2,4,...,10},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$2$, $4$,$6$,$8$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

@@

      \addplot table {
        1000	0.074
        1050	0.059
        1100	0.068
        1150	0.075
        1200	0.102
        1250	0.085
        1300	0.096
        1350	0.103
        1400	0.088
        1450	0.114  
      }; \addlegendentry{prpu-SML, dense};

      \addplot table {
        1000	0.035
        1050	0.037
        1100	0.043
        1150	0.044
        1200	0.051
        1250	0.065
        1300	0.058
        1350	0.068
        1400	0.059
        1450	0.069  
      }; \addlegendentry{prpu-Java2, dense};

      \addplot table {
        1000	0.046
        1050	0.05
        1100	0.048
        1150	0.059
        1200	0.056
        1250	0.056
        1300	0.058
        1350	0.062
        1400	0.062
        1450	0.066
      }; \addlegendentry{prpu-Java1, dense};

      \addplot table {
        1000	0.034
        1050	0.035
        1100	0.039
        1150	0.042
        1200	0.052
        1250	0.052
        1300	0.054
        1350	0.057
        1400	0.064
        1450	0.066  
      }; \addlegendentry{prpu-C++, dense};

      \addplot table {
        1000	0.006
        1050	0.004
        1100	0.006
        1150	0.005
        1200	0.007
        1250	0.007
        1300	0.007
        1350	0.007
        1400	0.007
        1450	0.008
      }; \addlegendentry{prpu-C, dense};
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	0.356
        1500	0.805
        2000	1.539
        2500	2.43
        3000	3.28
        3500	4.639
        4000	5.61
        4500	7.198
        5000	8.904
        5500	11.302
      }; \addlegendentry{edka-SML, wash};

      \addplot table {
        1000	0.105
        1500	0.228
        2000	0.385
        2500	0.466
        3000	0.7
        3500	0.992
        4000	1.194
        4500	1.503
        5000	1.735
        5500	2.243
      }; \addlegendentry{edka-Java, wash};

      \addplot table {
        1000	1.185
        1500	3.524
        2000	6.457
        2500	11.509
        3000	17.529
        3500	26.185
        4000	36.828
        4500	48.614
        5000	86.449
        5500	89.661
      }; \addlegendentry{prpu-SML, wash};

      \addplot table {
        1000	11.515
        1500	37.224
        2000	60.226
        2500	96.657
        3000	134.77
        3500	199.812
        4000	328.824
        4500	383.112
        5000	745.695
        5500	661.721
      }; \addlegendentry{prpu-Java2, wash};

      \addplot table {
        1000	0.654
        1500	1.626
        2000	3.096
        2500	5.313
        3000	8.572
        3500	12.552
        4000	18.103
        4500	18.646
        5000	40.456
        5500	39.012
      }; \addlegendentry{prpu-Java1, wash};

      \addplot table {
        1000	0.906
        1500	2.708
        2000	5.083
        2500	8.792
        3000	12.951
        3500	19.075
        4000	27.466
        4500	35.964
        5000	61.839
        5500	67.039
      }; \addlegendentry{prpu-C++, wash};

      \addplot table {
        1000	0.006
        1500	0.015
        2000	0.029
        2500	0.042
        3000	0.063
        3500	0.084
        4000	0.115
        4500	0.144
        5000	0.183
        5500	0.223
      }; \addlegendentry{prpu-C, wash};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {2,4,...,10},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$2$, $4$,$6$,$8$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	28.6
        1050	42.725
        1100	45.527
        1150	56.67
        1200	57.768
        1250	78.733
        1300	89.811
        1350	103.254
        1400	80.91
        1450	87.823
      }; \addlegendentry{edka-SML, acnet};

      \addplot table {
        1000	21.355
        1050	23.84
        1100	27.647
        1150	36.513
        1200	35.793
        1250	40.851
        1300	45.18
        1350	49.515
        1400	60.096
        1450	65.875
      }; \addlegendentry{edka-Java, acnet};

      \addplot table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; \addlegendentry{prpu-SML, acnet};

      \addplot table {
        1000	0.069
        1050	0.08
        1100	0.066
        1150	0.094
        1200	0.091
        1250	0.094
        1300	0.101
        1350	0.209
        1400	0.16
        1450	0.185
      }; \addlegendentry{prpu-Java2, acnet};

      \addplot table {
        1000	0.081
        1050	0.112
        1100	0.091
        1150	0.151
        1200	0.141
        1250	0.135
        1300	0.16
        1350	0.29
        1400	0.21
        1450	0.269
      }; \addlegendentry{prpu-Java1, acnet};

@@

      \addplot table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; \addlegendentry{prpu-C, acnet};
    \end{axis}
  \end{tikzpicture}

  \caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
  \end{figure}

>>>>

  \begin{figure}[!h]
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.515,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

@@

      \addplot table {
        1000 .005   
        1500 .013  
        2000 .024  
        2500 .037  
        3000 .066 
        3500 .077 
        4000 .096 
        4500 .146 
        5000 .194 
        5500 .192    
      }; \addlegendentry{prpu-SML, sparse};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {1,4,...,16},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$1$,$4$,$8$,$12$,$16$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

@@

      \addplot table {
        1000	0.074
        1050	0.059
        1100	0.068
        1150	0.075
        1200	0.102
        1250	0.085
        1300	0.096
        1350	0.103
        1400	0.088
        1450	0.114  
      }; \addlegendentry{prpu-SML, dense};
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {3000, 6000, 10500, 13500, 16500},
        ytick = {0.1,1,10,50,100},
        xticklabels = {$3k$, $6k$, $10k$, $13k$, $16k$},
        yticklabels = {$\text{\ \,}0.1$,$1$,$10$,$50$,$100$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting

      \addplot table {
        3000	1.185
        4500	3.524
        6000	6.457
        7500	11.509
        9000	17.529
        10500	26.185
        12000	36.828
        13500	48.614
        15000	86.449
        16500	89.661
      }; \addlegendentry{prpu-SML, wash};

      \addplot table {
        3000	0.906
        4500	2.708
        6000	5.083
        7500	8.792
        9000	12.951
        10500	19.075
        12000	27.466
        13500	35.964
        15000	61.839
        16500	67.039
      }; \addlegendentry{prpu-C++, wash};

      \addplot table {
        3000	0.006
        4500	0.015
        6000	0.029
        7500	0.042
        9000	0.063
        10500	0.084
        12000	0.115
        13500	0.144
        15000	0.183
        16500	0.223
      }; \addlegendentry{prpu-C, wash};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {0.01, 0.1, 0.2, 0.5, 1},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.52,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; \addlegendentry{prpu-SML, acnet};

@@

      \addplot table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; \addlegendentry{prpu-C, acnet};
    \end{axis}
  \end{tikzpicture}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {16000,19000,23000,27000,30000},
        ytick = {0.1,1,5,10,25},
        xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
        yticklabels = {$\text{\ \,}0.1$, $1$,$5$,$10$,$25$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.49,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        16000	3.602
        17600	4.223
        19200	4.839
        20800	8.201
        22400	8.273
        24000	13.426
        25600	10.089
        27200	15.889
        28800	16.431
        30400	21.437
      }; \addlegendentry{prpu-SML, genrmf};

      \addplot table {
        16000	4.51
        17600	4.804
        19200	5.899
        20800	8.052
        22400	8.448
        24000	11.555
        25600	8.878
        27200	13.999
        28800	12.99
        30400	13.791
      }; \addlegendentry{prpu-C++, genrmf};

      \addplot table {
        16000	0.009
        17600	0.012
        19200	0.015
        20800	0.021
        22400	0.021
        24000	0.019
        25600	0.023
        27200	0.028
        28800	0.026
        30400	0.026
      }; \addlegendentry{prpu-C, genrmf};
    \end{axis}
  \end{tikzpicture}
  \caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
  \end{figure}
